\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{color}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{lastpage}
\usepackage{enumitem}
%\usepackage[a4paper, top = 1in, bottom = 1in, left=1in,right=1in]{geometry}
\usepackage{tikz}
\usepackage{tikz-qtree}
\usepackage{listingsutf8}
\usepackage[hidelinks]{hyperref}

\begin{document}
\begin{center}
  \textbf{\huge{\scshape{Peter Heilbo Ratgen}}}\\ 
  \vspace{0.2cm}
  \small +4531330916 $|$
  \href{mailto:peter@pratgen.dk}{\underline{peter@pratgen.dk}} $|$
  \href{https://github.com/ratgen }{\underline{github}} $|$
  \href{https://pratgen.dk}{\underline{pratgen.dk}} $|$
  \href{https://www.linkedin.com/in/peter-ratgen-a1236529/}{\underline{linkedin}}
\end{center}
\vspace{0.5cm}

\begin{flushright}
  \today
\end{flushright}
\begin{flushleft}
\textbf{To:}\newline
University of Southern Denmark \newline
Campusvej 55 \newline
5230 Odense M
\end{flushleft}
\vspace{0.5cm}

To whom it may concern, \vspace{\baselineskip}

I am writing to apply for the three‑year engineering position in hardware and
software for robotic systems at SDU Robotics. With a bachelor’s and master’s in
Software Engineering from SDU and my current role as Engineer at SDU Medical
Robotics, I have built and maintained full‑stack applications (Next.js, React,
FastAPI), data‑collection clients in C++/Qt, and C#/.NET systems—always in close
collaboration with hardware teams and clinical partners. I also developed a
foundation in linear algebra, statistics, and discrete mathematics through my SDU
coursework.
\vspace{\baselineskip}

My experience includes integrating AI models into production workflows, and
designing intuitive user interfaces with a focus on user experience. I am
proficient in Typescript, C/C++ and Python, and have a proven track record of
working independently, as well as mentoring students and collaborating with
industry. I thrive on solving complex problems creatively, take ownership of my
projects, and communicate fluently in English and Danish. \vspace{\baselineskip}

I am excited by SDU Robotics’ continued focus on application‑oriented research and
development. \vspace{\baselineskip}

Feel free to contact me by phone or email at any time. \vspace{\baselineskip}

\begin{flushleft}
Best regards 

\vspace{\baselineskip} Peter Heilbo Ratgen
\end{flushleft}


\end{document}
