\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[danish]{babel}
\usepackage[T1]{fontenc}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{color}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{lastpage}
\usepackage{enumitem}
\usepackage[a4paper, top = 1in, bottom = 1in, left=1in,right=1in]{geometry}
\usepackage{tikz}
\usepackage{tikz-qtree}
\usepackage{listingsutf8}
\usepackage[hidelinks]{hyperref}

\newcommand{\tabitem}{~~\llap{\textbullet}~~}

\newcommand{\resumeSubheading}[4]{
  \noindent\begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\ \vspace{-3pt} 
    \textit{\small#3} & \textit{\small #4} 
  \end{tabular*}\vspace{7pt}
}

\begin{document}
\begin{center}
  \textbf{\huge{\scshape{Peter Heilbo Ratgen}}}\\ 
  \vspace{0.2cm}
  \small 31330916 $|$
  \href{mailto:peter@pratgen.dk}{\underline{peter@pratgen.dk}} $|$
  \href{https://github.com/PeterRatgen }{\underline{github}} $|$
  \href{https://pratgen.dk}{\underline{pratgen.dk}} $|$
  \href{https://www.linkedin.com/in/peter-ratgen-a1236529/}{\underline{linkedin}}
\end{center}

\noindent\large{\scshape{Education}} \newline
\noindent{\rule[0.3cm]{\textwidth}{0.4pt}}

\resumeSubheading{University of Southern Denmark}{}{Software Engineering}{Sep.
2020 -- Jul. 2022}\\\vspace{0.25cm}
{\indent\small Currently taking these courses:}
  \vspace{-0.3cm}
  {\small 
  \begin{itemize}
  \setlength{\itemsep}{-1pt}
    \item Statistical Data Analysis
    \item Human Computer Interaction
    \item Semesterproject: Interactive Distributed Software Systems
      \subitem Creating a media player using HTML and JavaScript, working with
      docker images and kubernetes. Interacting with other teams through APIs.
\end{itemize}} \vspace{0.3cm}


\resumeSubheading{University of Southern Denmark}{}{Computer Science}{Sep. 2017
-- Mar. 2020}\\\vspace{0.25cm} 
{\indent\small Completed 130 ECTS towards a Computer Science bachelors degree,
completed courses in:}
  \vspace{-0.3cm}
  {\footnotesize 
  \begin{itemize}
  \setlength{\itemsep}{-1pt}
    \item Discrete Methods for Computer Science
    \item Introduction to Programming
    \item Algorithms and Data Structures
    \item Database Design and Programming
    \item Concurrent Programming
    \item Networks and Security
    \item Computer architecture and system programming
    \item Linear algebra with applications
    \item Operating Systems
    \item Data mining and machine learning
    \item Formal Languages and Data Processing
    \item Software Engineering
\end{itemize}}
\vspace{0.3cm}

\resumeSubheading{Odense Tekniske Gymnasium}{}{Higher Technical
Examination}{Aug. 2014 -- Jul. 2017}
{\small \begin{itemize}\vspace{-0.25cm}
  \setlength{\itemsep}{-1pt}
  \item Specialized study area: Communication/IT A, Design B
  \item Technical science: Technical Sciences A, Electricity
    \subitem\footnotesize Worked with the PIC microcontroller.
\end{itemize}}
\vspace{0.5cm}

\noindent\large{\scshape{Acquired Skills}} \newline
\noindent{\rule[0.3cm]{\textwidth}{0.4pt}}

{\noindent\small\textbf{Languages:} Python, Java, Lua, JavaScript, Postgres SQL,
HTML/CSS, C}\newline
{\noindent\small\textbf{Tools:} Vim, Git, Bash}
\vspace{0.5cm}

\noindent\large{\scshape{Previous Jobs}} \newline
\noindent{\rule[0.3cm]{\textwidth}{0.4pt}}
\resumeSubheading{Boogies}{}{Cleaner}{Sep. 2018 -- Present}


\end{document}
